The promise of community-driven preprints in ecology and evolution

### 2024-10-13 ms/ms.qmd
C27

```{r, fig-summary}
#| label: fig-summary
#| fig-cap: "Summary of articles posted to *EcoEvoRxiv*. A) Number of articles (preprints and postprints) published on *EcoEvoRxiv* between 2018 and 2023. *EcoEvoRxiv* was established in June 2018 before the launch in November 2018. Notable milestones include *EcoEvoRxiv* transitioning to the California Digital Library (CDL), the acceptance of preprints and postprints in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of the preprints and postprints uploaded to *EcoEvoRxiv*, inferred from the country of affiliation of the submitting author; C) Taxa used/covered in the articles posted to *EcoEvoRxiv* (n = 1080 articles); D) Types of preprints accepted on *EcoEvoRxiv* (n = 620 articles). E) Academic age of authors posting to *EcoEvoRxiv* along with the gender of the submitting author. Values lower than zero are indicative of authors who uploaded preprints before their first scientific publication in a journal. Map base source:  R Package "maps" v.3.4.2. Shapefile: Natural Earth https://www.naturalearthdata.com/about/terms-of-use/."

@@

Empirical research articles are still the most common type of article submitted to *EcoEvoRxiv* (`r sum_types[sum_types$type == "research article",]$perc`%), followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]D). Currently, *EcoEvoRxiv* does not host many reports, particularly from government or industry, but has formed fruitful partnerships with the International Union for Conservation of Nature (IUCN). For example, IUCN Red-list Ecosystem Reports are now posted to *EcoEvoRxiv* and our community has been able to work closely with the IUCN to ensure these documents meet the IUCN requirements. We would encourage authors to consider posting books, book chapters, and reports to ensure that they are openly accessible and more easily found. Accepted *EcoEvoRxiv* submissions are given a unique DOI and are indexed on Google Scholar.

>>>>

```{r, fig-summary}
#| label: fig-summary
#| fig-cap: "Summary of articles posted to *EcoEvoRxiv*. A) Number of articles (preprints and postprints) published on *EcoEvoRxiv* between 2018 and 2023. *EcoEvoRxiv* was established in June 2018 before the launch in November 2018. Notable milestones include *EcoEvoRxiv* transitioning to the California Digital Library (CDL), the acceptance of preprints and postprints in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of the preprints and postprints uploaded to *EcoEvoRxiv*, inferred from the country of affiliation of the submitting author; C) Taxa used/covered in the articles posted to *EcoEvoRxiv* (n = 1080 articles covering relevant taxa); D) Types of preprints accepted on *EcoEvoRxiv* (n = 620 articles). E) Academic age of authors posting to *EcoEvoRxiv* along with the gender of the submitting author. Values lower than zero are indicative of authors who uploaded preprints before their first scientific publication in a journal. Map base source:  R Package "maps" v.3.4.2. Shapefile: Natural Earth https://www.naturalearthdata.com/about/terms-of-use/."

@@

Empirical research articles are still the most common type of article submitted to *EcoEvoRxiv* (`r sum_types[sum_types$type == "research article",]$perc`%), followed by reviews and meta-analyses (`r sum_types[sum_types$type == "reviews and meta-analyses",]$perc`%) and opinion papers (`r sum_types[sum_types$type == "opinion",]$perc`%) ([@fig-summary]D). Currently, *EcoEvoRxiv* does not host many reports, particularly from government or industry, but has formed fruitful partnerships with the International Union for Conservation of Nature (IUCN). For example, IUCN Red-list Ecosystem Reports are now posted to *EcoEvoRxiv* and our community has been able to work closely with the IUCN to ensure these documents meet the IUCN requirements. We would encourage authors to consider posting books, book chapters, and reports to ensure that they are openly accessible and more easily found. Accepted *EcoEvoRxiv* submissions are given a unique DOI and are indexed on Google Scholar. Having a unique DOI means that the article can be accessed in perpetuity. If the preprint becomes published, then this DOI is merged with the published DOI.
